Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-04-28 scripts/MouseSexDiffApril20_2020.Rmd
Adding of text to tables. SHINICHI to check / change

```{r include=FALSE}
# Quick pre-check before doing plots
metacombo %>%
  group_by(GroupingTerm) %>%
  dplyr::summarize(MeanCVR = mean(lnCVR), MeanVR = mean(lnVR), MeanRR = mean(lnRR))
```

### Supplemental Table 3: "Meta-analysis results"

@@

### Performing meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR)

@@

```
### Supplemental Table 4
MISSING table descpition. Refer to in ms.
```{r Table4}
kable(overall2, , digits = 3) %>%
 kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

# Metameta_Fig3_female.sig #(Figure 5B left panel)
```
#### Supplemental Table 5
Table o

@@

kable(mf_sig) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "300px")
```

####  Figure 5
Sex biases in trait values across trait groups (Step J in Figure 3). The panels in A show differences in the number of affected traits, in variance (lnCVR) and means (lnRR), where there is a significant difference between the sexes (i.e CI not overlapping zero). Panel B shows results for the sex bias in those traits that differ between the sexes (second-order meta-analysis). Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability). The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.

@@

# Supplemental Plots
## Figure S1 
### Including lnVR
### Count data, including lnVR (Fig S1 panel A)

@@

## Heterogeneity Table and Plot
### Supplemental Table 5: "Heterogeneity within groups"
 SZ: missing a desciption so far. MISSING!! Also: rearrange table structure, what does this show??
```{r}
kable(heterog6, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

>>>>

```{r include=FALSE}
# Quick pre-check before doing plots
metacombo %>%
  group_by(GroupingTerm) %>%
  dplyr::summarize(MeanCVR = mean(lnCVR), MeanVR = mean(lnVR), MeanRR = mean(lnRR))

```
### Supplemental Table 3: "Meta-analysis results"

@@

### Performing meta-analyses 
Three for each of the 9 grouping terms: lnCVR, lnVR, lnRR

@@

```
### Supplemental Table 4: "Meta-analysis on Functional Trait Groups"
SHINICHI
This table summarizes our overall meta-analyses on the functional trait group level ("GroupingTerm"). Results for lnCVR, lnVR and lnRR and their respective upper and lower 95% CI's, standard error and I2 values are provided.
```{r Table4}
kable(overall2, digits = 3) %>%
 kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

# Metameta_Fig3_female.sig #(Figure 5B left panel)
```
### Supplemental Table 5
SHINICHI
This table provides some of the data plotted in Figures 5 and Figure S2. Here, we provide an overview over meta-analysis results performed on traits that were significantly biased to either sex. This table summarizes findings for both sexes and the respective functional trait groups.

@@

kable(mf_sig, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "300px")
```

###  Figure 5
Sex biases in trait values across trait groups (Step J in Figure 3). The panels in A show differences in the number of affected traits, in variance (lnCVR) and means (lnRR), where there is a significant difference between the sexes (i.e CI not overlapping zero). Panel B shows results for the sex bias in those traits that differ between the sexes (second-order meta-analysis). Triangles represent sex bias in means (response ratio) and black circles differences in the coefficient of variation ratio (mean-adjusted variability). The orange-red bars represent trait groups with a female bias, blue-green bars male-biased traits.

@@

# Supplemental Plots and Tables
### Figure S1 
#### Including lnVR
#### Count data, including lnVR (Fig S1 panel A)

@@

## Heterogeneity Table and Plot
### Supplemental Table 6: "Heterogeneity within groups"
SHINICHI
This table summarizes our findings on heterogeneity due to institutions and mouse strains. These results are based on meta-analyses on sigma^2 and errors for mouse strains and centers (Institutions), following the identical workflow from above.

het <- heterog6 %>%
  pivot_wider(names_from = parameter, values_from = value:ci.h) %>%
  rename(lnCVR = value_heteroCVR, lnCVR_lower = ci.low_heteroCVR, lnCVR_higher = ci.high_heteroCVR, 
       lnVR = value_heteroVR, lnVR_lower = ci.low_heteroVR, lnVR_higher = ci.high_heteroVR, 
       lnRR = value_heteroRR, lnRR_lower = ci.low_heteroRR, lnRR_higher = ci.high_heteroRR,
       CVR = mean_heteroCVR, VR = mean_heteroVR, RR = mean_heteroRR,  CVR_lower = ci.l_heteroCVR, 
       VR_lower = ci.l_heteroVR, RR_lower = ci.l_heteroRR, 
       CVR_higher = ci.h_heteroCVR, VR_higher = ci.h_heteroVR, RR_higher = ci.h_heteroRR) %>%
  select(1,2,5,8,3,6,9,4,7,10,14,17,20,15,18,21,16,19,22)

kable(het, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
